Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-16 Draft/input.tex
Updated input section

\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
        \label{cut:1}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
        \begin{align}
        \label{cut:2}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
        \label{cut:3}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        Typically, on the two jets with largest transverse-momentum VBS cuts are applied.
        These are an invariant-mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
        The nominal value of these cuts if not stated explicitly read:
        \begin{align}
        \label{cut:4}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.
\end{itemize}

>>>>

\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
        \label{cut:1}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
        \begin{align}
        \label{cut:2}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
        \label{cut:3}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated.
        These are an in\-vari\-ant mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
        The nominal value of these cuts if not stated explicitly read:
        \begin{align}
        \label{cut:4}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.
\end{itemize}
